Estimating the Dynamics of SPARQL Query Results Using Binary Classification

### 2019-11-13 main.tex
Updating title case

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks, 
    linkcolor={black},
    citecolor={black}, urlcolor={black},
    pdftitle={Estimating the dynamics of SPARQL query results using binary classification},    % title
    pdfauthor={Alberto Moya Loustaunau, Aidan Hogan},     % author
    pdfsubject={QuWeDa @ ISWC 2019},   % subject of the document
    pdfkeywords={SPARQL;} {Linked Data;} {Dynamics;} {Wikidata;}, % list of keywords
}

@@

\begin{document}
%
\title{Estimating the dynamics of SPARQL query results using binary classification
%\thanks{This work was supported by CONICYT PFCHA, Doctorado Becas Chile/2017 -- 72180000, the Millennium Institute for Foundational Research on Data (IMFD) and FONDECYT Grant No. 1181896.}
}
%
\titlerunning{Estimating the dynamics of SPARQL query results}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Alberto Moya Loustaunau\and Aidan Hogan}
%
%\authorrunning{A. Moya and A. Hogan}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{IMFD; DCC, University of Chile\\
\email{\{amoya,ahogan\}@dcc.uhile.cl}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We address the problem of estimating when the results of an input SPARQL query over dynamic RDF datasets will change. We evaluate a framework that extracts features from the query and/or from past versions of the target dataset and inputs them into binary classifiers to predict whether or not the results for a query will change at a fixed point in the near future. For this evaluation, we create a gold standard based on 23 versions of Wikidata and a curated collection of 221 SPARQL queries. Our results show that the quality of predictions possible using (only) features based on the query structure and lightweight statistics of the predicate dynamics -- though capable of beating a random baseline -- are not competitive with results obtained using (more costly to derive) knowledge of the complete historical changes in the query results.

>>>>

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks, 
    linkcolor={black},
    citecolor={black}, urlcolor={black},
    pdftitle={Estimating the Dynamics of SPARQL Query Results Using Binary Classification},    % title
    pdfauthor={Alberto Moya Loustaunau, Aidan Hogan},     % author
    pdfsubject={QuWeDa @ ISWC 2019},   % subject of the document
    pdfkeywords={SPARQL;} {Linked Data;} {Dynamics;} {Wikidata;}, % list of keywords
}

@@

\begin{document}
%
\title{Estimating the Dynamics of SPARQL Query Results Using Binary Classification
%\thanks{This work was supported by CONICYT PFCHA, Doctorado Becas Chile/2017 -- 72180000, the Millennium Institute for Foundational Research on Data (IMFD) and FONDECYT Grant No. 1181896.}
}
%
\titlerunning{Estimating the Dynamics of SPARQL Query Results}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Alberto Moya Loustaunau\and Aidan Hogan}
%
%\authorrunning{A. Moya and A. Hogan}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{IMFD; DCC, University of Chile\\
\email{\{amoya,ahogan\}@dcc.uhile.cl}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We address the problem of estimating when the results of an input SPARQL query over dynamic RDF datasets will change. We evaluate a framework that extracts features from the query and/or from past versions of the target dataset and inputs them into binary classifiers to predict whether or not the results for a query will change at a fixed point in the near future. For this evaluation, we create a gold standard based on 23 versions of Wikidata and a curated collection of 221 SPARQL queries. Our results show that the quality of predictions possible using (only) features based on the query structure and lightweight statistics of the predicate dynamics -- though capable of beating a random baseline -- are not competitive with results obtained using (more costly to derive) knowledge of the complete historical changes in the query results.
